On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-10-01 paper2.tex

This analytical model describes the number of RHs expected in our model per unit
luminosity and per unit comoving volume $V_{\rmn{c}}$, i.e., $\rmn{d}^2N(L,z)
/\rmn{d}V_{\rmn{c}}\rmn{d}L$. Hence the cumulative number of RHs above a given flux
limit $F$ is given by the integral
\begin{equation}
N(>F)  =  \int_{z_1}^{z_2} \int_{L(F)}^{\infty} 
\frac{\rmn{d}^2N(L,z)}{\rmn{d}V_{\rmn{c}}\rmn{d}L}\,
\frac{\rmn{d}V_{\rmn{c}}}{\rmn{d}z}\, \rmn{d}z\, \rmn{d}L ,
\label{eq:NtotRH}
\end{equation}
where $L(F) = 4 \pi D(z)^2 F$ and $D(z)$ is the luminosity distance to an RH at
redshift $z$.  The result is shown in the left panel of
Fig.~\ref{fig:RLF_120_flux} for the model realization described in
Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters (black solid
line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
\geq 29.25$. Our redshift integration extends from $z_{1} = 0.018$, the redshift
of the closest known RH in Perseus, to $z_{2} = 2$. As shown in
Fig.~\ref{fig:RLF_120_flux}, already redshifts $z\gtrsim1$ do not
significantly contribute to the flux function. Additionally, there are large
theoretical uncertainties since our gas model is not calibrated for these
redshifts (and implied low-mass range) and very little is observationally known
about diffuse radio emission on group scales in particularly at these redshifts,
which motivates our upper redshift limit. \qc{\bf Note also that at these high redshifts, 
the analytical model for the evolving RLF gives spurious counts due to the 
non-perfect matching with simulations in this regime.}

>>>>

This analytical model describes the number of RHs expected in our model per unit
luminosity and per unit comoving volume $V_{\rmn{c}}$, i.e., $\rmn{d}^2N(L,z)
/\rmn{d}V_{\rmn{c}}\rmn{d}L$. Hence the cumulative number of RHs above a given flux
limit $F$ is given by the integral
\begin{equation}
N(>F)  =  \int_{z_1}^{z_2} \int_{L(F)}^{\infty} 
\frac{\rmn{d}^2N(L,z)}{\rmn{d}V_{\rmn{c}}\rmn{d}L}\,
\frac{\rmn{d}V_{\rmn{c}}}{\rmn{d}z}\, \rmn{d}z\, \rmn{d}L ,
\label{eq:NtotRH}
\end{equation}
where $L(F) = 4 \pi D(z)^2 F$ and $D(z)$ is the luminosity distance to an RH at
redshift $z$.  The result is shown in the left panel of
Fig.~\ref{fig:RLF_120_flux} for the model realization described in
Section~\ref{sec:4} with a 10 per cent fraction of radio-loud clusters (black
solid line). We limit the integral to luminosities $\log_{10} L_{120~\rmn{MHz}}
\geq 29.25$. Our redshift integration extends from $z_{1} = 0.018$, the redshift
of the closest known RH in Perseus, to $z_{2} = 2$. As shown in
Fig.~\ref{fig:RLF_120_flux}, already redshifts $z\gtrsim1$ do not significantly
contribute to the flux function. Additionally, there are large theoretical
uncertainties since our gas model is not calibrated for these redshifts (and
implied low-mass range) and very little is observationally known about diffuse
radio emission on group scales in particularly at these redshifts, which
motivates our upper redshift limit. {\bf Note also that at these high redshifts,
  the analytical fit to the evolving RLF slightly overproduces the simulation
  number counts.}
